Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-05 paper.tex
Wordsmithing

In \textit{scikit-learn}, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem like bare representations of data when compared to
more object-oriented representations\footnote{Weka~\citep{hall2009weka} is an
example of a toolkit-specific object-oriented data representation.}, they bring
the prime advantage of allowing us to rely on all NumPy and SciPy vector
operations -- often orders of magnitude faster that the corresponding Python
loops -- while allowing us at the same time to keep the code short and readable.
From a practical point of view, these formats also provide a bunch of data
loading and conversion tools which make them very easy to use in many
contexts\footnote{For tasks where the inputs are text files or semi-structured
objects, we provide \textit{vectorizer} objects that efficiently convert such
data to the NumPy or SciPy formats.}. Finally, this design choice has also been
motivated by the fact that, given their pervasiveness in many other scientific
Python packages, many scientific users of Python are likely to be already used
to those formats, hence helping them to familiarize with the project.

>>>>

In \textit{scikit-learn}, we chose a representation of data that is as close as
possible to the matrix representation: datasets are encoded as NumPy
multidimensional arrays for dense data and as SciPy sparse matrices for sparse
data. While those may seem like bare and minimalistic data representations
when compared to more object-oriented
representations\footnote{Weka~\citep{hall2009weka} is an example of a toolkit-specific
object-oriented data representation.}, they bring the prime advantage
of allowing us to rely on all NumPy and SciPy vector operations -- often orders
of magnitude faster that the corresponding Python loops -- while allowing us at
the same time to keep the code short and readable. From a practical point of
view, these formats also provide a bunch of data loading and conversion tools
which make them very easy to use in many contexts\footnote{For tasks where the
inputs are text files or semi-structured objects, we provide \textit{vectorizer}
objects that efficiently convert such data to the NumPy or SciPy formats.}.
Finally, this design choice has also been motivated by the fact that, given
their pervasiveness in many other scientific Python packages, many scientific
users of Python are likely to be already familiar with those formats, hence helping
them to familiarize with the project.
